### 2023-12-18 manuscript.tex
add references [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/84a03aa1376ce7a4793ae4c2260615baa8ed7714.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/84a03aa1376ce7a4793ae4c2260615baa8ed7714/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/7248818486

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/84088b2f37c9a2d894b35f3c9aae1ab1282165c7/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/84088b2f37c9a2d894b35f3c9aae1ab1282165c7}{MMV-Lab/im2im-paper@84088b2}
on December 18, 2023.

@@

One of main directions for extending \emph{MMV\_Im2Im} is to pre-pack common bioimaging datasets as a Dataset module, so that DL researchers can use it for algorithm development and benchmarking, and new users can easily use it for learning microscopy image-to-image transformation. We will continue improving the functionalities of the package, such as supporting more models and methods, such as diffusion based models {[}\protect\hyperlink{ref-1A3yurr7m}{46}{]}, unsupervised denoising {[}\protect\hyperlink{ref-4vnyY9J9}{42}{]} or Imaginaire (\url{https://github.com/NVlabs/imaginaire}). Besides, we also plan to develop two auxiliary packages \emph{MMV\_Im2Im\_Auto} and \emph{MMV\_Im2Im\_Active}. In specific, when you have a reasonable amount of training data, \emph{MMV\_Im2Im\_Auto} will take advantage of the fact that MMV\_Im2Im is fully configurable with yaml files, and automatically generate a set of potentially good configurations, then find the optimal solution for you by cross validation. On the other hand, when you only have very limited training data, or even with only pseudo ground truth, \emph{MMV\_Im2Im\_Active} will help to build preliminary models from the limited training data, and gradually refine the model with human-in-the-loop by active learning {[}\protect\hyperlink{ref-jM3v1UjQ}{20}{]}. All the packages will also be wrapped into napari plugins {[}\protect\hyperlink{ref-YEMgt2T4}{48}{]} to allow no-code operation and therefore be more friendly to users without experience in programming.

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/84a03aa1376ce7a4793ae4c2260615baa8ed7714/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/84a03aa1376ce7a4793ae4c2260615baa8ed7714}{MMV-Lab/im2im-paper@84a03aa}
on December 18, 2023.

@@

One of main directions for extending \emph{MMV\_Im2Im} is to pre-pack common bioimaging datasets as a Dataset module, so that DL researchers can use it for algorithm development and benchmarking, and new users can easily use it for learning microscopy image-to-image transformation. We will continue improving the functionalities of the package, such as supporting more models and methods, such as diffusion based models {[}\protect\hyperlink{ref-1A3yurr7m}{46}{]}, unsupervised denoising {[}\protect\hyperlink{ref-4vnyY9J9}{42}{]} or Imaginaire {[}\protect\hyperlink{ref-vzOBQiEH}{47}{]}. Besides, we also plan to develop two auxiliary packages \emph{MMV\_Im2Im\_Auto} and \emph{MMV\_Im2Im\_Active}. In specific, when you have a reasonable amount of training data, \emph{MMV\_Im2Im\_Auto} will take advantage of the fact that MMV\_Im2Im is fully configurable with yaml files, and automatically generate a set of potentially good configurations, then find the optimal solution for you by cross validation. On the other hand, when you only have very limited training data, or even with only pseudo ground truth, \emph{MMV\_Im2Im\_Active} will help to build preliminary models from the limited training data, and gradually refine the model with human-in-the-loop by active learning {[}\protect\hyperlink{ref-jM3v1UjQ}{20}{]}. All the packages will also be wrapped into napari plugins {[}\protect\hyperlink{ref-YEMgt2T4}{48}{]} to allow no-code operation and therefore be more friendly to users without experience in programming.
